Visual Question Answering with DeepProbLog

### 2022-03-12 paper/paper.tex
Write a bit further

\subsection{Logical rule encodings}
% TODO optimizations in these logical rule encodings? Possible to change e.g. red_number_of_shapes(...) into number_of_shapes(red, ...)?

@@

The final thing required before commencing the training process, are the data loaders. The most challenging part here is the transformation from the generated data to specific query mappings and their outcome. One of the questions are chosen, and a correct mapping between a predicate in the logical rule encoding file and the answer is set up.

@@

>>>>

@@

The final thing (besides the logical rule encodings) required before commencing the training process, are the data loaders. The most challenging part here is the transformation from the generated data to specific query mappings and their outcome. One of the questions are chosen, and a correct mapping between a predicate in the logical rule encoding file and the answer is set up.

\subsection{Logical rule encodings}
Once the CNN belonging to a specific color has determined the position and the shape of that object, logical rules can deduce whether this object is located on the left hand side of the image, on the bottom side, and how many objects have the same shape. The logical rule program has been listed in Appendix \ref{appendix:logical_rule_encodings}

@@

\section{APPENDIX}
\subsection{Logical rule encodings}
\label{appendix:logical_rule_encodings}
% TODO put logical rules here
